Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-06-09 Journal/JAS Data Association/JAS_DataAssoc_rev1.tex
journal added

A variety of data association techniques are considered for close-proximity trajectories with varying performance.
Multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques involve a high computational load, especially when objects are in close proximity, making real-time implementation more difficult~\cite{MHT1,PHD1,PHD2}.
Many other techniques are based on the Kalman filter (KF) or the extended KF (EKF), which provide a framework for recursive data association techniques for easier real-time implementation.
There are two popular strategies among recursive approaches, namely \emph{hard decisions} and \emph{soft decisions}~\cite{JPDAF1}.
When the association between an object of interest and a measurement is assumed correct, this is referred to as a hard decision.
%A hard decision is when estimates are fully associated with measurements according to some metric between the estimates and the measurements.
For example, a common heuristic approach is known as the nearest neighbor filter (NNF), which uses a distance measure between each measurement and the predicted measurements of each potential object to determine likely associations.
%For example, a common heuristic approach is known as the nearest neighbor filter (NNF), which uses the Mahalanobis distance between each measurement and the predicted measurements of each potential object to determine likely associations.
The measurement with the smallest Mahalanobis distance is considered as the correct one~\cite{NN2}.
However, when estimates are in close proximity, there is a high likelihood of making incorrect associations, which may be detrimental to the estimated states, so this technique is avoided in the analysis of this paper.

@@

However, the popular JPDAF approaches suffer from a common pitfall, namely sub-optimality.
More explicitly, Kalman filters are considered optimal in the sense that the estimator gain is selected to minimize the mean square error of the estimated state, or equivalently a measure of posterior uncertainty.
%More explicitly, Kalman filters are considered optimal in the sense that the estimator gain is selected to minimize the posterior uncertainties.
In the current JPDAF applications, the Kalman gain is directly used in the measurement update processes, indeliberately assuming that the Kalman gain designed for a single object tracking is also optimal for multiple object tracking problems.

@@

Therefore, we propose a new coalescence-avoiding optimal JPDAF, referred to as the C-JPDAF, which is a systematic approach to remove coalescence by minimizing the weighted sum of the uncertainty and a similarity index between estimates. The prior work from~\cite{KauLovLee14} covers the concept in simple cases, assuming that only two objects are considered with a single measurement at each time step, and that the state and measurement are very similar. These assumptions are unrealistic in most scenarios.
%Therefore, we generalize the C-JPDAF algorithm in this paper to handle any number of objects and measurements, missed detections and measurements originating from extraneous clutter, and measurements with a much different interpretation than just the object states.
Therefore, we generalize the C-JPDAF algorithm in this paper to handle any number of objects and measurements, missed detections, measurements originating from extraneous clutter, and various types of measurements.

In short, the main contributions of this paper are (i) deriving the optimal JPDAF that minimizes the posterior uncertainties in estimation, and (ii) proposing a systematic approach to avoid data coalescence of multiple objects in close-proximity. The desirable features of the proposed approaches are illustrated by extensive numerical simulations with satellites in orbits.

@@

The Gaussian states are tracked with measurements; however, the measurement origins are unknown. Suppose that these measurements are unordered and possibly include spurious measurements and missed detections. Data association and filtering serves to estimate the state of the systems when there exist uncertainties in the system processes, the measurements, and the measurement originations. In this paper, the popular joint probabilistic data association filtering is improved in two distinct ways in the subsequent sections.

@@

Suppose that there are $n_r$ measurements at the $k$-th time step where $n_r$ is finite and nonzero and may be greater or less than the number of objects $n_t$ due to extraneous clutter or missed detections.
Because all equations in this subsection take place at the $k$-th time step, this subscript is removed from the equations.
For the $i$-th object, the predicted measurement $\hat z_i\in\Re^m$ is based on the a priori state estimate $\hat x_{i}^-$ according to \refeqn{zlin},
%\footnote{Note that for nonlinear systems where $z_i = h_i(x_i)$, then $\hat z_i = h_i(\hat x_{i}^-)$ replaces \refeqn{zlin} and the linearized matrix $H_i=\deriv{h_i}{x_i}\bigg|_{x_i=\hat x_{i}^-}$ is used for the remaining equations.\label{fn:nonlinsys}}
\begin{align}
\label{eqn:zhatlin}
\hat z_i = H_i\hat x_{i}^-.
\end{align}
The innovation, often referred to as the residual, $e_{i,j}\in\Re^m$ is defined as the difference between the $j$-th measurement and the predicted measurement of the $i$-th object, and it is given by
\begin{align}
e_{i,j} = z_j - \hat z_i.\label{eqn:eij}
\end{align}
%where the true measurement is expected to be
%\begin{align}
%z_i=h(x_i)+v_i, \quad H_i=\frac{\partial h}{\partial x}\bigg|_{x=\hat x_{i}^- }.
%\end{align}
%Given the uncertainty of the measurements represented with covariance matrix $R_i$, t
For the $j$-th measurement, the $i$-th a priori innovation covariance matrix $S_{i,j}\in\Re^{m\times m}$ represents the uncertainty between the $i$-th measurement estimate and its true measurement, defined as
%The a priori innovation covariance matrix $S_{i}\in\Re^{m\times m}$ for all innovations corresponding to the $i$-th object is defined as \EditTL{(Is it for the covariance of $e_{ii}$? Not sure.. What is the meaning of `the covariance matrix for all innovations...')}
\begin{align}
S_{i,j}&=\mathrm{E}[e_{i,j} e_{i,j}^T]=\mathrm{E}[\left((H_ix_i+v_i)-H_i\hat x_{i}^-\right)\left((H_ix_i+v_i)-H_i\hat x_{i}^-\right)^T]\nonumber\\
&=H_{i}P_{i}^{-}H_{i}^T+R_{j},\label{eqn:S}
\end{align}
where it is commonly assumed that $R_j$ is uniform for all measurements, but the subsequent equations make no such assumption.

@@

Next, we define a measurement origination model. Let $\beta_{i,j}\in\Re$ be the probability that the $j$-th measurement originates from the $i$-th object. 
%Let $\beta_{i,j}$ be the probability that the $i$-th system is associated with measurement $j$.
%Two techniques may be applied to solve for every $\beta_{i,j}$, both of which require the innovation and its covariance (defined later) and information on detection probabilities, which are assumed known. The first technique is applied in the standard JPDAF that calculates the true association probabilities from~\cite[Eq. 9.(45-46)]{TrackDataAssoc}. However, the computation required with a standard JPDAF is inconsistent with the capabilities of the computational resources to account for an arbitrary number of objects to be tracked~\cite{Bar1990}.
Several approaches have been proposed to approximate the association probability $\beta_{i,j}$ for the JPDAF.
This paper adopts the expressions given in~\cite{Bar1990}, and they are summarized as follows.

@@

%A modified version of the JPDA, commonly known as the ``Cheap JPDA'', provides a simpler approximation of the likelihood $\beta_{i,j}$.
%The equations below are adopted from~\cite[Eq. 1.(1-2)]{Bar1990}.

Let $G_{i,j}\in\Re$ be a simplified scaled density function between the $i$-th measurement estimate and the $j$-th measurement,
% variable which takes a very similar form as the Gaussian probability density function
\begin{align}
G_{i,j}=\frac1{\sqrt{\det{S_{i,j}}}}\exp{\{-\frac12e_{i,j}^TS_{i,j}^{-1}e_{i,j}\}}.
\end{align}
%This is used to calculate intermediate variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$
%\begin{align}
%\mathcal{S}_{ti}=\sum\limits_{j\in J}G_{i,j}, 
%\quad 
%\mathcal{S}_{ri}=\sum\limits_{i\in I}G_{i,j}.
%\end{align}
Then a close approximation of the probability that the $i$-th system is associated with the $j$-th measurement is
\begin{align}
\label{eqn:betaDef}
\beta_{i,j}=\frac{G_{i,j}}{\sum\limits_{l=1}^{n_r}G_{il}+\sum\limits_{l=1}^{n_t}G_{lj}-G_{i,j}+B},
\end{align}
where $B=0$ corresponds to rare extraneous measurements and missed detections. When these are prevalent, a fixed value of $B$ found from simulations was shown to perform well in various applications~\cite{Bar1990}. In this paper, we assume that at most a single measurement may originate from a single object, and missed detections and measurements originating from extraneous clutter are considered insignificant, so $B=0$ is used to determine joint association probability.

@@

%\EditTL{(The above writing has several issues that the reviewers of ACC15 mentioned. (i) There is no indication on the dimension of variables. For example is $G_{i,j}$ a scalar or a vector; (ii) there are several variables, such as $e_{i,j}$ or $S_i$ that were used before defining them explicitly. Saying that it is the innovation and the a priori innovation covariance is not sufficient. Ideally, we have to define a variable before using it; (iii) The definition of $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$ is unclear. Is $t$ also an indexed variable?; (iv) Do you really have to introduce the set $I$ and $J$. It is causing more confusion as several other variations of $J$ will appear later in this paper. Would it be more concise to rewrite it as $\sum_{j=1}^{n_r}$?; (v) Do we really have to introduce the variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$. If they are used here only, there is no need to define them. It's better to substitute (6) into (7). Usually, a new variable or symbol is defined, only if it has an important meaning, or it is used repeatedly later; (vi) how is $B$ defined, and what's the dimension of it. Give the explicit definition, or at least cite something. The given explanation raises more questions. }

The weighted sum of all innovations associated with the object $i$ is defined as ${\bar{e}}_{i}={\sum\limits_{j=1}^{n_r} \beta_{i,j}e_{i,j}}\in\Re^m$.
The innovations serve to update the resulting posterior state estimate $\hat x^+_{i}$ with the gain matrix $K_i\in\Re^{n\times m}$~\cite{TrackDataAssoc},
%~\cite[Eq. 6-(25-26)]{TrackDataAssoc}
\begin{align}
\hat x^+_{i}= \hat x^-_{i}+K_{i}{\bar{e}}_{i}.\label{eqn:KalEst}
\end{align}
The conventional JPDAF chooses $K_i=P^-_iH_i^TS_i^{-1}$ (assuming $S_i$ is fixed for all measurements) as the gain from the Kalman filter.
In this paper, we show that the Kalman gain does not actually minimize the posterior uncertainty in probabilistic data association filtering, and we derive the new \textit{optimal} gain $K_i$.

Let the probability that $i$-th object is \textit{not} associated with any measurement be $\beta_{i,0}=1-{\sum_{j=1}^{n_r} \beta_{i,j}}\in\Re$. The case when $\beta_{i,0}=1$ implies that the $i$-th estimate is \emph{not} associated with any measurement completely, i.e., the $i$-th object is not measured by any sensor with the probability of one. In such trivial cases, there is no measurement update, i.e., $\hat x^+_i=\hat x^-_i$.

Next we consider when $\beta_{i,0}\neq1$, i.e., $0\leq\beta_{i,0}<1$.
Let the a priori and a posteriori errors be defined as
\begin{align}
\label{eqn:ErrFuns}
\tilde x_i^-=\hat x_i^--x_i,
\quad
\tilde x_i^+=\hat x_i^+-x_i,
\end{align}
respectively.
Then, using \refeqn{zlin}, \refeqn{zhatlin}, \refeqn{eij}, \refeqn{ErrFuns}, and the difference between \refeqn{KalEst} and \refeqn{xestapriori}, we have
\begin{align}
\tilde x_i^+&=
%\hat x_i^+-\hat x_i^-+\tilde x_i^-
%\nonumber\\&=
K_i\sum_{j=1}^{n_r}\beta_{i,j}(z_j-\hat z_i)+\tilde x_i^-
\nonumber\\&=
%K_i\sum_{j=1}^{n_r}\beta_{i,j}(H_ix_i+v_j-H_i\hat x_i^-)+\tilde x_i^-
%\nonumber\\&=
%-K_iH_i\tilde x_i^-\sum_{j=1}^{n_r}\beta_{i,j}+K_i\sum_{j=1}^{n_r}\beta_{i,j}v_j+\tilde x_i^-
%\nonumber\\&=
(I-(1-\beta_{i,0})K_iH_i)\tilde x_i^-+K_i\sum_{j=1}^{n_r}\beta_{i,j}v_j.
\end{align}

The resulting posterior covariance $P^+_{i}\in\Re^{n\times n}$ is defined as
%~\cite[Eq. D-32 and D-33]{TrackDataAssoc}
\begin{align}
\label{eqn:JPDAFCov}
P_i^+&=\text{E}[\tilde x_i^+\tilde x_i^{+T}]
%\nonumber\\&=
%\text{E}[
%\{(I-(1-\beta_{i,0})K_iH_i)\tilde x_i^-+K_i\sum_{j=1}^{n_r}\beta_{i,j}v_j\}\{(I-(1-\beta_{i,0})K_iH_i)\tilde x_i^-+K_i\sum_{j=1}^{n_r}\beta_{i,j}v_j\}^T
%]
%\nonumber\\&=
%(I-(1-\beta_{i,0})K_iH_i)\text{E}[\tilde x_i^-\tilde x_i^{-T}](I-(1-\beta_{i,0})K_iH_i)^T
%+
%K_i\text{E}[\sum_{j=1}^{n_r}\beta_{i,j}v_j\sum_{j=1}^{n_r}\beta_{i,j}v_j^T]K_i^T
\nonumber\\&=
(I-(1-\beta_{i,0})K_iH_i)P_i^-(I-(1-\beta_{i,0})K_iH_i)^T
+
K_i(\sum_{j=1}^{n_r}\beta^2_{i,j}R_j)K_i^T
\nonumber\\&=
P_i^--(1-\beta_{i,0})
(K_iH_iP_i^-+P_i^-H_i^TK_i^T)
+
K_iE_iK_i^T.
\end{align}
where $E_i\in\Re^{m\times m}$ is defined for convenience as
\begin{align}
\label{eqn:E}
E_i=\sum_{j=1}^{n_r}\beta^2_{i,j}R_j+(1-\beta_{i,0})^2H_iP_i^-H_i^T.
\end{align}
%$\tilde P_i\in\Re^{n\times n}$ is the portion of the $i$-th state covariance matrix due to the spread in the innovations
%\begin{align}
%\tilde P_i=&\ K_i\parenth{{\sum_{j=1}^{n_r} \beta_{i,j}e_{i,j}e_{i,j}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T}K_{i}^T,\label{eqn:tildeP}
%\end{align}
%and $P_i^c\in\Re^{n\times n}$ corresponds to the $i$-th posterior covariance if only a single measurement serves to update the $i$-th estimate~\cite{TrackDataAssoc}%, and it can be written as
%%We can define $P_i^c$ without any assumptions on $K_i$ (i.e., $K_i$ is not necessarily the Kalman gain, so the well-known Kalman covariance update equations are not valid here) as~\cite[Eq. 4.2-12]{OptEst1}
%\begin{align}
%P^c_i=&\ (I-K_iH_i)P^-_i(I-K_iH_i)^T+K_iR_iK_i^T\nonumber
%\\
%=&\ P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)+K_i(H_iP^-_iH_i^T+R_i)K_i^T,
%\label{eqn:GenCov}
%\end{align}
%which is commonly referred to as the \emph{Joseph form}, valid for \emph{any} gain matrix $K_i$~\cite{OptEst1}.
%Substituting \refeqn{tildeP} and \refeqn{GenCov} into \refeqn{JPDAFCov},% and rearranging,
%\begin{align}
%P^+_{i}=&\ \beta_{i,0}P^-_{i}+(1-\beta_{i,0})[P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
%\\
%&\ +K_i(H_iP^-_iH_i^T+R_i)K_i^T]+K_i\left({\sum_{j=1}^{n_r} \beta_{i,j}e_{i,j}e_{i,j}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T\right)K_{i}^T\nonumber
%\\
%%=&\ P^-_{i}-(1-\beta_{i,0})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)+K_i\left((1-\beta_{i,0})S_i+{\sum_{j=1}^{n_r} \beta_{i,j}e_{i,j}e_{i,j}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T\right)K_i^T\nonumber%asdf
%%\\
%=&\ P^-_{i}-(1-\beta_{i,0})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)+K_iE_iK_i^T,\label{eqn:CovExpanded}
%\end{align}
%where the symmetric matrix $E_i=E_i^T\in\Re^{m\times m}$ is defined as
%\begin{align}
%E_i=(1-\beta_{i,0})S_i+{\sum_{j=1}^{n_r} \beta_{i,j}e_{i,j}e_{i,j}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T,\label{eqn:E}
%\end{align}
%and it corresponds to an innovation covariance that accounts for the possibility that more than a single measurement may update the $i$-th estimate.
Since \refeqn{JPDAFCov} and \refeqn{E} make no assumptions on $K_i$, this form is valid for \emph{any} gain $K_i$.

>>>>

A variety of data association techniques are considered for close-proximity trajectories with varying performance.
Multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques involve a high computational load, especially when objects are in close proximity, making real-time implementation more difficult~\cite{MHT1,PHD1,PHD2}.
Many other techniques are based on the Kalman filter (KF) or the extended KF (EKF), which provide a framework for recursive data association techniques for easier real-time implementation.
There are two popular strategies among recursive approaches, namely \emph{hard decisions} and \emph{soft decisions}~\cite{JPDAF1}.
When the association between an object of interest and a measurement is assumed correct, this is referred to as a hard decision.
%A hard decision is when estimates are fully associated with measurements according to some metric between the estimates and the measurements.
For example, a common heuristic approach is known as the nearest neighbor filter (NNF), which uses a distance measure (e.g. Euclidean, Mahalanobis) between each measurement and the predicted measurements of each potential object to determine likely associations.
%For example, a common heuristic approach is known as the nearest neighbor filter (NNF), which uses the Mahalanobis distance between each measurement and the predicted measurements of each potential object to determine likely associations.
The measurement with the smallest distance is considered as the correct one~\cite{NN2}.
However, when estimates are in close proximity, there is a high likelihood of making incorrect associations, which may be detrimental to the estimated states, so this technique is avoided in the analysis of this paper.

@@

However, the popular JPDAF approaches suffer from a common pitfall, namely sub-optimality.
More explicitly, Kalman filters are considered optimal in the sense that the estimator gain is selected to minimize the mean square error of the estimated state, or equivalently a measure of posterior uncertainty.
%More explicitly, Kalman filters are considered optimal in the sense that the estimator gain is selected to minimize the posterior uncertainties.
In the current JPDAF applications, the Kalman gain is directly used in the measurement update processes, indeliberately assuming that the Kalman gain designed for a single object tracking is also optimal for multiple object tracking problems with soft decisions.

@@

Therefore, we propose a new coalescence-avoiding optimal JPDAF, referred to as the C-JPDAF, which is a systematic approach to remove coalescence by minimizing the weighted sum of the uncertainty and a similarity index between estimates. The prior work from~\cite{KauLovLee14} covers the concept in simple cases, assuming that only two objects are considered with a single measurement at each time step, and that the object state and measurement are very similar. These assumptions are unrealistic in most scenarios.
%Therefore, we generalize the C-JPDAF algorithm in this paper to handle any number of objects and measurements, missed detections and measurements originating from extraneous clutter, and measurements with a much different interpretation than just the object states.
Therefore, we generalize the C-JPDAF algorithm in this paper to handle any number of objects and measurements, missed detections, measurements originating from extraneous clutter, and various types of measurements.

In short, the main contributions of this paper are (i) deriving the optimal JPDAF that minimizes the posterior mean square error and uncertainties in estimation, and (ii) proposing a systematic approach to avoid data coalescence of multiple objects in close-proximity. The desirable features of the proposed approaches are illustrated by extensive numerical simulations with satellites in orbits.

@@

The Gaussian states are tracked with measurements; however, the measurement origins are unknown. Suppose that these measurements are unordered and possibly include spurious measurements and missed detections. Data association and filtering serves to estimate the state of the systems when there exist uncertainties in the system processes, the measurements, and the measurement origins. In this paper, the popular joint probabilistic data association filtering is improved in two distinct ways in the subsequent sections.

@@

Suppose that there are $n_r$ measurements at the $k$-th time step where $n_r$ is finite and nonzero and may be greater or less than the number of objects $n_t$ due to extraneous clutter or missed detections.
Because all equations in this subsection take place at the $k$-th time step, this subscript is removed from the equations.
For the $i$-th object, the predicted measurement $\hat z_i\in\Re^m$ is based on the a priori state estimate $\hat x_{i}^-$ according to \refeqn{zlin},
%\footnote{Note that for nonlinear systems where $z_i = h_i(x_i)$, then $\hat z_i = h_i(\hat x_{i}^-)$ replaces \refeqn{zlin} and the linearized matrix $H_i=\deriv{h_i}{x_i}\bigg|_{x_i=\hat x_{i}^-}$ is used for the remaining equations.\label{fn:nonlinsys}}
\begin{align}
\label{eqn:zlin}
\hat z_i = H_i\hat x_{i}^-.
\end{align}
The innovation, often referred to as the residual, $e_{ij}\in\Re^m$ is defined as the difference between the $j$-th measurement and the predicted measurement of the $i$-th object, and it is given by
\begin{align}
e_{ij} = z_j - \hat z_i.\label{eqn:eij}
\end{align}
%where the true measurement is expected to be
%\begin{align}
%z_i=h(x_i)+v_i, \quad H_i=\frac{\partial h}{\partial x}\bigg|_{x=\hat x_{i}^- }.
%\end{align}
%Given the uncertainty of the measurements represented with covariance matrix $R_i$, t
The $i$-th a priori innovation covariance matrix $S_i\in\Re^{m\times m}$ represents the uncertainty between the $i$-th measurement estimate and its true measurement, defined as
%The a priori innovation covariance matrix $S_{i}\in\Re^{m\times m}$ for all innovations corresponding to the $i$-th object is defined as \EditTL{(Is it for the covariance of $e_{ii}$? Not sure.. What is the meaning of `the covariance matrix for all innovations...')}
\begin{align}
S_{i}&=\mathrm{E}[e_{ij} e_{ij}^T]=\mathrm{E}[\left((H_ix_i+v_i)-H_i\hat x_{i}^-\right)\left((H_ix_i+v_i)-H_i\hat x_{i}^-\right)^T]\nonumber\\
&=H_{i}P_{i}^{-}H_{i}^T+R_{i}.\label{eqn:S}
\end{align}

@@

Next, we define a measurement origination model. Let $\beta_{ij}\in\Re$ be the probability that the $j$-th measurement originates from the $i$-th object. 
%Let $\beta_{ij}$ be the probability that the $i$-th system is associated with measurement $j$.
%Two techniques may be applied to solve for every $\beta_{ij}$, both of which require the innovation and its covariance (defined later) and information on detection probabilities, which are assumed known. The first technique is applied in the standard JPDAF that calculates the true association probabilities from~\cite[Eq. 9.(45-46)]{TrackDataAssoc}. However, the computation required with a standard JPDAF is inconsistent with the capabilities of the computational resources to account for an arbitrary number of objects to be tracked~\cite{Bar1990}.
Several approaches have been proposed to approximate the association probability $\beta_{ij}$ for the JPDAF.
This paper adopts the expressions given in~\cite{Bar1990}, and they are summarized as follows.

@@

%A modified version of the JPDA, commonly known as the ``Cheap JPDA'', provides a simpler approximation of the likelihood $\beta_{ij}$.
%The equations below are adopted from~\cite[Eq. 1.(1-2)]{Bar1990}.

Let $G_{ij}\in\Re$ be a simplified scaled density function between the $i$-th measurement estimate and the $j$-th measurement,
% variable which takes a very similar form as the Gaussian probability density function
\begin{align}
G_{ij}=\frac1{\sqrt{\det{S_{i}}}}\exp{\{-\frac12e_{ij}^TS_{i}^{-1}e_{ij}\}}.
\end{align}
%This is used to calculate intermediate variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$
%\begin{align}
%\mathcal{S}_{ti}=\sum\limits_{j\in J}G_{ij}, 
%\quad 
%\mathcal{S}_{ri}=\sum\limits_{i\in I}G_{ij}.
%\end{align}
Then a close approximation of the probability that the $i$-th system is associated with the $j$-th measurement is
\begin{align}
\label{eqn:betaDef}
\beta_{ij}=\frac{G_{ij}}{\sum\limits_{l=1}^{n_r}G_{il}+\sum\limits_{l=1}^{n_t}G_{lj}-G_{ij}+B},
\end{align}
where $B=0$ corresponds to rare extraneous measurements and missed detections. When these are prevalent, a fixed value of $B$ found from simulations was shown to perform well in various applications~\cite{Bar1990}. In this paper, we assume that at most a single measurement may originate from a single object, and missed detections and measurements originating from extraneous clutter are considered insignificant, so $B=0$ is used to determine joint association probability.

@@

%\EditTL{(The above writing has several issues that the reviewers of ACC15 mentioned. (i) There is no indication on the dimension of variables. For example is $G_{ij}$ a scalar or a vector; (ii) there are several variables, such as $e_{ij}$ or $S_i$ that were used before defining them explicitly. Saying that it is the innovation and the a priori innovation covariance is not sufficient. Ideally, we have to define a variable before using it; (iii) The definition of $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$ is unclear. Is $t$ also an indexed variable?; (iv) Do you really have to introduce the set $I$ and $J$. It is causing more confusion as several other variations of $J$ will appear later in this paper. Would it be more concise to rewrite it as $\sum_{j=1}^{n_r}$?; (v) Do we really have to introduce the variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$. If they are used here only, there is no need to define them. It's better to substitute (6) into (7). Usually, a new variable or symbol is defined, only if it has an important meaning, or it is used repeatedly later; (vi) how is $B$ defined, and what's the dimension of it. Give the explicit definition, or at least cite something. The given explanation raises more questions. }

The weighted sum of all innovations associated with the object $i$ is defined as ${\bar{e}}_{i}={\sum\limits_{j=1}^{n_r} \beta_{ij}e_{ij}}\in\Re^m$.
The innovations serve to update the resulting posterior state estimate $\hat x^+_{i}$ with the gain matrix $K_i\in\Re^{n\times m}$~\cite{TrackDataAssoc},
%~\cite[Eq. 6-(25-26)]{TrackDataAssoc}
\begin{align}
\hat x^+_{i}= \hat x^-_{i}+K_{i}{\bar{e}}_{i}.\label{eqn:KalEst}
\end{align}
The conventional JPDAF chooses $K_i=P^-_iH_i^TS_i^{-1}$ as the gain from the Kalman filter.
In this paper, we show that the Kalman gain does not actually minimize the posterior uncertainty in probabilistic data association filtering, and we derive the new \textit{optimal} gain $K_i$.

Let the probability that $i$-th object is \textit{not} associated with any measurement be $\beta_{0,i}=1-{\sum_{j=1}^{n_r} \beta_{ij}}\in\Re$. The case when $\beta_{0,i}=1$ implies that the $i$-th estimate is \emph{not} associated with any measurement completely, i.e., the $i$-th object is not measured by any sensor with the probability of one. In such trivial cases, there is no measurement update, i.e., $\hat x^+_i=\hat x^-_i$ and $P_i^+=P_i^-$.

Next we consider when $\beta_{0,i}\neq1$, i.e., $0\leq\beta_{0,i}<1$.
The resulting posterior state covariance $P^+_{i}\in\Re^{n\times n}$ is derived in~\cite[Eq. D-32 and D-33]{TrackDataAssoc}, where this term is defined as $\text{E}[(x_i-\hat x_i^+)(x_i-\hat x_i^+)^T]$ and the resulting solution is derived from the law of total expectation considering each innovation individually. Then, $P^+_{i}$ is simplified to
\begin{align}
\label{eqn:JPDAFCov}
P^+_{i}=&\ \beta_{0,i}P^-_{i}+(1-\beta_{0,i})P_i^c+\tilde P_i,
\end{align}
where $\tilde P_i\in\Re^{n\times n}$ is the portion of the $i$-th state covariance matrix due to the spread in the innovations
\begin{align}
\tilde P_i=&\ K_i\parenth{{\sum_{j=1}^{n_r} \beta_{ij}e_{ij}e_{ij}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T}K_{i}^T,\label{eqn:tildeP}
\end{align}
and $P_i^c\in\Re^{n\times n}$ corresponds to the $i$-th posterior covariance if only a single measurement serves to update the $i$-th estimate.
This covariance term is defined as $P^c_i=(I-K_iH_i)P_i^-$ according to~\cite[Eq. D-27]{TrackDataAssoc}, or $P^c_i=P_i^--K_iS_iK_i^T$ according to~\cite[Eq. 43]{JPDAF1}, where both equivalent versions assume that the Kalman gain is used. The derivation of $P^c_i$ is the only occurence in \refeqn{JPDAFCov} where the Kalman gain assumption is enforced. Without such an assumption, we have%, and it can be written as
%We can define $P_i^c$ without any assumptions on $K_i$ (i.e., $K_i$ is not necessarily the Kalman gain, so the well-known Kalman covariance update equations are not valid here) as~\cite[Eq. 4.2-12]{OptEst1}
\begin{align}
P^c_i=&\ (I-K_iH_i)P^-_i(I-K_iH_i)^T+K_iR_iK_i^T\nonumber
\\
=&\ P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)+K_i(H_iP^-_iH_i^T+R_i)K_i^T,
\label{eqn:GenCov}
\end{align}
which is commonly referred to as the \emph{Joseph form}, valid for \emph{any} gain matrix $K_i$~\cite{OptEst1}.
Substituting \refeqn{tildeP} and \refeqn{GenCov} into \refeqn{JPDAFCov},% and rearranging,
\begin{align}
P^+_{i}=&\ \beta_{0,i}P^-_{i}+(1-\beta_{0,i})[P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_i(H_iP^-_iH_i^T+R_i)K_i^T]+K_i\left({\sum_{j=1}^{n_r} \beta_{ij}e_{ij}e_{ij}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T\right)K_{i}^T\nonumber
\\
%=&\ P^-_{i}-(1-\beta_{0,i})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)+K_i\left((1-\beta_{0,i})S_i+{\sum_{j=1}^{n_r} \beta_{ij}e_{ij}e_{ij}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T\right)K_i^T\nonumber%asdf
%\\
=&\ P^-_{i}-(1-\beta_{0,i})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)+K_iE_iK_i^T,\label{eqn:CovExpanded}
\end{align}
where the symmetric matrix $E_i=E_i^T\in\Re^{m\times m}$ is defined as
\begin{align}
E_i=(1-\beta_{0,i})S_i+{\sum_{j=1}^{n_r} \beta_{ij}e_{ij}e_{ij}^T-{\bar{e}}_{i}}{\bar{e}}_{i}^T,\label{eqn:E}
\end{align}
and it corresponds to an innovation covariance that accounts for the possibility that more than a single measurement may update the $i$-th estimate.
Because \refeqn{CovExpanded} is based on the Jordan form, this equation yields an accurate $P^+_{i}$ for \emph{any} gain $K_i$.

As with the Kalman filter, we choose the uncertainty cost function $J_{P_i}\in\Re$ to be the trace of the posterior covariance,
\begin{align}
\label{eqn:JpIntro}
J_{P_i}=\tr{P_i^+}.
\end{align}
We choose the gain to minimize $J_{P_i}$, where the necessary condition for a local minimum is given by
\begin{align}
0=\frac{\partial\tr{P^+_i}}{\partial K_i}=-2(1-\beta_{0,i})P^-_iH_i^T+2K_iE_i.\label{eqn:Uncertainty0}
\end{align}
Therefore the optimal gain is selected as
\begin{align}
K_i&=(1-\beta_{0,i})P^-_iH_i^TE_i^{-1}.\label{eqn:GainK}
\end{align}
%As with the Kalman filter, we choose the estimation gain to minimize the magnitude of the posterior covariance measured by $\tr{P_i^+}$.
%The first derivative necessary condition for optimality requires that
%\begin{align}
%0&=\frac{\partial\tr{P^+_i}}{\partial K_i},\nonumber
%\\
%&=-2(1-\beta_{0,i})\frac{\partial\tr{K_iH_iP^-_i}}{\partial K_i}+\frac{\partial\tr{K_iE_iK_i^T}}{\partial K_i},\nonumber
%\\
%&=-2(1-\beta_{0,i})P^-_iH_i^T+2K_iE_i.\label{eqn:Uncertainty0}
%\end{align}
%%Therefore the optimal gain is given by
%%\begin{align}
%%K_i&=(1-\beta_{0,i})P^-_iH_i^TE_i^{-1}.\label{eqn:GainK}
%%\end{align}
%Solving \refeqn{Uncertainty0} to satisfy necessary condition for optimality,
%\begin{align}
%K_i&=(1-\beta_{0,i})P^-_iH_i^TE_i^{-1}.\label{eqn:GainK}
%\end{align}
%The Hessian

Finally, \refeqn{GainK} is substituted into \refeqn{CovExpanded} to obtain a simplified posterior state covariance matrix
%\begin{align}
%\label{eqn:PNotSimplified}
%P^+_{i}&=P^-_{i}-(1-\beta_{0,i})^2P^-_iH_i^TE_i^{-1}H_iP^-_i,
%\end{align}
%which may be simplified in two ways
\begin{align}
P^+_{i}&=P^-_{i}-K_iE_iK_i^T, \quad \mbox{or equivalently}\label{eqn:JPDAFPostCovSymmetricUpdate}
\\
P^+_{i}&=\left(I-(1-\beta_{0,i})K_iH_i\right)P^-_i.\label{eqn:JPDAFPostCovSimpleUpdate}
\end{align}
